This is a title

### 2019-01-04 paper/data_template.tex
base level table is filled out, probably time to start writing :(

Classifier&TPR&FPR&AUC&CV10 Acc. \\ \hline
{% for clf_label in CLF_LABELS %}
    {{ clf_label }}&{{ '%0.2f' % CLASSIFIERS[clf_label].TEST_TPR_RATE }}&{{ '%0.2f' % CLASSIFIERS[clf_label].TEST_FPR_RATE }}&{{ '%0.2f' % CLASSIFIERS[clf_label].ROC_AUC }}&{{ '%0.2f+-%0.2f' % (CLASSIFIERS[clf_label].CV10_BALANCED_ACCURACY[0], CLASSIFIERS[clf_label].CV10_BALANCED_ACCURACY[1]) }} \\
{% endfor %}

>>>>

\multirow{2}{*}{Classifier}&\multicolumn{4}{c||}{Performance}&\multicolumn{4}{c}{Rank Median(Mean)} \\ \cline{2-9}
&TPR&FPR&AUC&CV10 Acc.&Overall (n={{ TEST_COUNTS.OVERALL }})&
VUS (n={{ TEST_COUNTS.VARIANT_OF_UNCERTAIN_SIGNIFICANCE }})&
Likely Path. (n={{ TEST_COUNTS.LIKELY_PATHOGENIC }})&Pathogenic (n={{ TEST_COUNTS.PATHOGENIC }}) \\ \hline
{% for clf_label in CLF_LABELS %}
    {{ clf_label }}&
    {{ '%0.2f' % CLASSIFIERS[clf_label].TEST_TPR_RATE }}&
    {{ '%0.2f' % CLASSIFIERS[clf_label].TEST_FPR_RATE }}&
    {{ '%0.2f' % CLASSIFIERS[clf_label].ROC_AUC }}&
    {{ '%0.2f+-%0.2f' % (CLASSIFIERS[clf_label].CV10_BALANCED_ACCURACY[0], CLASSIFIERS[clf_label].CV10_BALANCED_ACCURACY[1]) }}&
    {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS.OVERALL), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS.OVERALL)) }}&
    {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS.VARIANT_OF_UNCERTAIN_SIGNIFICANCE), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS.VARIANT_OF_UNCERTAIN_SIGNIFICANCE)) }}&
    {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS.LIKELY_PATHOGENIC), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS.LIKELY_PATHOGENIC)) }}&
    {{ '%0.1f (%0.2f)' % (np.median(CLASSIFIERS[clf_label].TEST_RANKINGS.PATHOGENIC), np.mean(CLASSIFIERS[clf_label].TEST_RANKINGS.PATHOGENIC)) }} \\
{% endfor %}
